Dewlap color variation in \textit{Anolis sagrei} is maintained among habitats within islands of the West Indies

### 2021-05-29 ms/sections/figures.tex
island maps and island figures refurbished

\begin{figure}[H]
	\centering
	\includegraphics[width=\textwidth]{figures/Abaco.png}
	\caption{Comparison of dewlap coloration across habitats on Abaco. (A) Confusion matrix showing the proportion of lizards from each (true) habitat reassigned to each (predicted) habitat by the random forests, based on the first four within-island principal components and averaged across replicates. Each column sums to one. (B) One-dimensional sensitivity analysis showing the relative importance (mean decrease in accuracy) of the various wavelengths in random forest classification of the whole spectrum. (C) Reflectance profiles of all the dewlaps on the island. (D) Within-island principal component scores across habitats. Bars indicate significant contrasts. *, $P < 0.05$; **, $P < 0.01$; ***, $P < 0.001$. (E) How reflectance profiles map onto the within-island principal components. (F) Map of the island with the sampling sites colored by habitat. (G) Geographical distance between sites where significant differences were detected in within-island principal component scores (Wilcoxon test, Benjamini-Hochberg correction, $P < 0.05$), including only pairs of sites whose habitats were involved in between-habitat dewlap differences.}
	\label{fig:Abaco}
\end{figure}

>>>>

\begin{figure}[H]
	\centering
	\includegraphics[width=\textwidth]{figures/Abaco_2.2.png}
	\caption{Comparison of dewlap coloration across habitats on Abaco. (A) Map of the island with the sampling sites colored by habitat. (B) Reflectance profiles of all the dewlaps on the island. (C) How reflectance profiles map onto the within-island principal components. (D) Confusion matrix showing the proportion of lizards from each (true) habitat reassigned to each (predicted) habitat by the random forests, based on the first four within-island principal components and averaged across replicates. Each column sums to one. (E) Within-island principal component scores across habitats. Bars indicate significant contrasts. *, $P < 0.05$; **, $P < 0.01$; ***, $P < 0.001$.}
	\label{fig:Abaco}
\end{figure}

### 2021-05-29 ms/sections/suppfigures.tex
island maps and island figures refurbished

\begin{figure}[H]
	\centering
	\includegraphics[width=\textwidth]{figures/all_maps.png}
	\caption{Maps of the islands. (A) Map of the West Indies with sampled islands highlighted in black. (B) Sampling sites within islands colored after their respective habitat-types.}
	\label{fig:maps}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=\textwidth]{figures/Bimini.png}
	\caption{Comparison of dewlap coloration across habitats on Bimini. Legend is as per Figure \ref{fig:Abaco}.}
	\label{fig:Bimini}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=\textwidth]{figures/CaymanBrac.png}
	\caption{Comparison of dewlap coloration across habitats on Cayman Brac. Legend is as per Figure \ref{fig:Abaco}.}
	\label{fig:CaymanBrac}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=\textwidth]{figures/Eleuthera.png}
	\caption{Comparison of dewlap coloration across habitats on Eleuthera. Legend is as per Figure \ref{fig:Abaco}.}
	\label{fig:Eleuthera}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=\textwidth]{figures/LittleCayman.png}
	\caption{Comparison of dewlap coloration across habitats on Little Cayman. Legend is as per Figure \ref{fig:Abaco}.}
	\label{fig:LittleCayman}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=\textwidth]{figures/LongIsland.png}
	\caption{Comparison of dewlap coloration across habitats on Long Island. Legend is as per Figure \ref{fig:Abaco}.}
	\label{fig:LongIsland}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=\textwidth]{figures/NorthAndros.png}
	\caption{Comparison of dewlap coloration across habitats on North Andros. Legend is as per Figure \ref{fig:Abaco}.}
	\label{fig:NorthAndros}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=\textwidth]{figures/SouthAndros.png}
	\caption{Comparison of dewlap coloration across habitats on South Andros. Legend is as per Figure \ref{fig:Abaco}.}
	\label{fig:SouthAndros}
\end{figure}

>>>>

\begin{figure}[H]
	\centering
	\includegraphics[width=\textwidth]{figures/island_maps_white_2.0.png}
	\caption{Maps of the islands. (A) Map of the West Indies with sampled islands highlighted in black. (B) Sampling sites within islands colored after their respective habitat-types.}
	\label{fig:maps}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=\textwidth]{figures/Abaco_supplement_1.0b.png}
	\caption{Comparison of dewlap coloration across habitats on Abaco, with extended results. (A--E) Legend as per Figure \ref{fig:Abaco}. (F) One-dimensional sensitivity analysis showing the relative importance (mean decrease in accuracy) of the various wavelengths in random forest classification of the whole spectrum. (G) Geographical distance between sites where significant differences were detected in within-island principal component scores (Wilcoxon test, Benjamini-Hochberg correction, $P < 0.05$), including only pairs of sites whose habitats were involved in between-habitat dewlap differences.}
	\label{fig:Abaco_supplement}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=\textwidth]{figures/Bimini_supplement.png}
	\caption{Comparison of dewlap coloration across habitats on Bimini. Legend is as per Figure \ref{fig:Abaco_supplement}.}
	\label{fig:Bimini}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=\textwidth]{figures/CaymanBrac_supplement.png}
	\caption{Comparison of dewlap coloration across habitats on Cayman Brac. Legend is as per Figure \ref{fig:Abaco_supplement}.}
	\label{fig:CaymanBrac}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=\textwidth]{figures/Eleuthera_supplement.png}
	\caption{Comparison of dewlap coloration across habitats on Eleuthera. Legend is as per Figure \ref{fig:Abaco_supplement}.}
	\label{fig:Eleuthera}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=\textwidth]{figures/LittleCayman_supplement.png}
	\caption{Comparison of dewlap coloration across habitats on Little Cayman. Legend is as per Figure \ref{fig:Abaco_supplement}.}
	\label{fig:LittleCayman}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=\textwidth]{figures/LongIsland_supplement.png}
	\caption{Comparison of dewlap coloration across habitats on Long Island. Legend is as per Figure \ref{fig:Abaco_supplement}.}
	\label{fig:LongIsland}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=\textwidth]{figures/NorthAndros_supplement.png}
	\caption{Comparison of dewlap coloration across habitats on North Andros. Legend is as per Figure \ref{fig:Abaco_supplement}, but without panel G.}
	\label{fig:NorthAndros}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=\textwidth]{figures/RaggedIsland_supplement.png}
	\caption{Comparison of dewlap coloration across habitats on Ragged Island. Legend is as per Figure \ref{fig:Abaco_supplement}, but without panel G.}
	\label{fig:RaggedIsland}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=\textwidth]{figures/SouthAndros_supplement.png}
	\caption{Comparison of dewlap coloration across habitats on South Andros. Legend is as per Figure \ref{fig:Abaco_supplement}.}
	\label{fig:SouthAndros}
\end{figure}
